%-------------------------
% Resume in Latex
% Author : Jake Gutierrez / modified for ATS optimization
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\setlength{\footskip}{4.1pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-2pt}\raggedright\bfseries\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% ATS: ensure machine-readable unicode
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \normalfont{\small#3} & \normalfont{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
\begin{document}

%----------HEADING — plain text, no icons, fully ATS-parseable----------
\begin{center}
    {\Huge \scshape Aashish Dhawan} \\ \vspace{3pt}
    \small +1\,352-871-4686 $\cdot$
    \href{mailto:aashudhawan@gmail.com}{aashudhawan@gmail.com} $\cdot$
    \href{https://linkedin.com/in/aashish-dhawan/}{linkedin.com/in/aashish-dhawan} $\cdot$
    \href{https://github.com/dhawan98}{github.com/dhawan98} $\cdot$
    \href{https://dhawan98.github.io}{dhawan98.github.io}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\vspace{2pt}
\small{Machine Learning Engineer and PhD researcher with \textbf{5+ years} building and deploying ML systems
across NLP, computer vision, and multimodal AI. Experienced fine-tuning large language models (LLaMA, GPT-4,
mBART-50) with LoRA/PEFT, designing \textbf{RAG} pipelines, and shipping production-grade AI at
\textbf{ExxonMobil} and for 5,000+ end users. Published at \textbf{ACL 2026} (shared task winner) and
EACL 2026. Seeking Applied Scientist, ML Engineer, or Data Scientist roles.}
\vspace{-6pt}

%-----------SKILLS — ATS-priority order----------
\section{SKILLS}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.0in, label={}]
  \small{\item{
    \textbf{Languages:} Python, SQL, Java, C++, R \\
    \textbf{ML Frameworks:} PyTorch, TensorFlow, Hugging Face Transformers, scikit-learn, XGBoost \\
    \textbf{LLMs \& NLP:} GPT-4, LLaMA, Gemini, Qwen2.5-VL, mBART-50, Fine-tuning (LoRA/PEFT),
      Retrieval-Augmented Generation (RAG), LangChain, Multilingual NLP, Low-Resource MT \\
    \textbf{Computer Vision:} CLIP, SAM, DINO, Object Detection, Image Segmentation, Diffusion Models \\
    \textbf{Tools \& MLOps:} FastAPI, AWS, Docker, Git, FAISS, Streamlit, Pandas, NumPy \\
  }}
\end{itemize}
\vspace{-22pt}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart
\vspace{-2pt}

\resumeSubheading
  {Computational Data Scientist Intern}{May 2026 -- Present}
  {ExxonMobil}{Houston, TX}
  \resumeItemListStart
    \resumeItem{Developed Python XAI pipelines that generate counterfactual explanations and feature-level
    attributions for industrial optimization models, enabling operations teams to interrogate and validate
    model-driven decisions in production workflows.}
    \resumeItem{Built what-if simulation tooling allowing stakeholders to perturb model inputs, evaluate
    sensitivity of optimization outputs, and reason about model behavior without ML expertise---reducing
    reliance on black-box predictions for high-stakes industrial decisions.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {Machine Learning Researcher}{May 2024 -- Present}
  {Data Science \& Research Lab, University of Florida}{Gainesville, FL}
  \resumeItemListStart
    \resumeItem{Engineered a few-shot object detection system (CLIP + SAM + DINO + Adaptive Feature Transfer
    + OHAC clustering) achieving \textbf{15\% accuracy improvement} over CLIP baselines in 1--10-shot regimes,
    with interpretable concept-level visual explanations per prediction.}
    \resumeItem{Built a production \textbf{RAG pipeline} for low-resource Indigenous language translation using
    Qwen2.5-VL image captioning, BM25 retrieval, and Gemini 2.5 Flash many-shot prompting; system
    \textbf{ranked 1st at AmericasNLP 2026 Shared Task (ACL)}.}
    \resumeItem{Fine-tuned multilingual \textbf{mBART-50} with distributed data-parallel (DDP) multi-GPU
    training, reducing training time by \textbf{50\%}; evaluated using chrF++ with full ablation studies
    published at EACL 2026.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {Adjunct Instructor}{Aug 2023 -- Present}
  {University of Florida}{Gainesville, FL}
  \resumeItemListStart
    \resumeItem{Designed and delivered Machine Learning and Programming Languages courses for
    \textbf{300+ students} per semester; developed assignments, rubrics, and project-based evaluations.}
    \resumeItem{Mentored capstone projects: LLM-powered chatbots, recommendation systems, and real-time
    computer vision pipelines.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {AI Engineer, Consultant}{Aug 2023 -- Apr 2024}
  {Atmosphere Apps}{Gainesville, FL}
  \resumeItemListStart
    \resumeItem{Engineered GPT-4 and Whisper-based NLP pipelines for prescription recommendation and
    multilingual transcription, improving matching accuracy by \textbf{20\%} for \textbf{5,000+} active users.}
    \resumeItem{Delivered audio/video transcription across 10+ languages at \textbf{95\% accuracy},
    producing structured summaries, topic extractions, and auto-generated quizzes at scale.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {Research Assistant}{Jan 2021 -- May 2023}
  {Graphics Imaging \& Light Measurement Lab, University of Florida}{Gainesville, FL}
  \resumeItemListStart
    \resumeItem{Developed deep learning pipelines for multispectral image synthesis, quantum simulation
    acceleration, and material-scattering prediction, reducing evaluation time by up to \textbf{82\%}.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {Visiting Researcher}{Dec 2019 -- Mar 2020}
  {UBTECH AI Lab, University of Sydney}{Sydney, Australia}
  \resumeItemListStart
    \resumeItem{Implemented multi-source domain adaptation (CNN backbone, shared encoder + domain-specific
    classifiers); achieved 71--98\% accuracy across 345 categories on a 0.6M-sample dataset.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeSubheading
  {Research Intern}{May 2019 -- Aug 2019}
  {Space Applications Center, ISRO}{Ahmedabad, India}
  \resumeItemListStart
    \resumeItem{Built a CNN--CRF semantic segmentation pipeline for satellite imagery (LISS-3 + POTSDAM),
    improving accuracy by 5\% and cutting inference from 36 hours to 0.2 seconds
    (\textbf{648,000$\times$ speedup}).}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-14pt}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
  {Ph.D. in Computer Science}{Aug 2025 -- May 2028 (Expected)}
  {University of Florida}{Gainesville, FL}

\resumeSubheading
  {M.S. in Computer Science}{Jan 2021 -- May 2023}
  {University of Florida}{Gainesville, FL}
\resumeItemListStart
  \resumeItem{\textbf{Coursework:} Natural Language Processing, Deep Learning for Computer Graphics,
  Trustworthy ML}
\resumeItemListEnd

\resumeSubheading
  {Bachelor of Technology in Computer Science}{Aug 2015 -- May 2019}
  {Kurukshetra University}{Haryana, India}

\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PUBLICATIONS (compact)-----------
\section{PUBLICATIONS}
\resumeItemListStart
  \resumeItem{Dhawan et al. ``Retrieval-Augmented Long-Context Translation for Cultural Image Captioning.''
  \emph{AmericasNLP @ ACL 2026.} \href{https://arxiv.org/abs/2605.20626}{arXiv:2605.20626}.
  \textbf{[Overall Shared Task Winner]}}
  \resumeItem{Dhawan et al. ``Improving Indigenous Language MT with Synthetic Data and Language-Specific
  Preprocessing.'' \emph{LoResMT @ EACL 2026.}
  \href{https://arxiv.org/abs/2601.03135}{arXiv:2601.03135}.}
  \resumeItem{Driggers-Ellis, \ldots, Dhawan et al. ``MultiScript30k: Multilingual Embeddings for
  Cross-Script Parallel Data.'' \href{https://arxiv.org/abs/2512.11074}{arXiv:2512.11074}.
  \emph{Under review, ACL Rolling Review.}}
  \resumeItem{Dhawan et al. ``Post Processing of Image Segmentation Using CRF.''
  \emph{IEEE INDIACom}, 2019.}
\resumeItemListEnd
\vspace{-14pt}

%-----------SELECTED PROJECTS-----------
\section{SELECTED PROJECTS}
\vspace{-8pt}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Explainable Few-Shot Object Detection (Indigenous Manuscripts)}
   $|$ \emph{PyTorch, CLIP, SAM, DINO, FastAPI}}{2025}
\resumeItemListStart
\vspace{2pt}
\resumeItem{Concept-based few-shot detection for Mixtec manuscripts using CLIP, SAM, DINO, and Adaptive
Feature Transfer; \textbf{15\% accuracy gain} over CLIP with hierarchical visual explanations per
prediction served via a FastAPI inference backend.}
\resumeItemListEnd

\vspace{-16pt}

\resumeProjectHeading
  {\textbf{RAGFlow: Documentation Assistant}
   $|$ \emph{Python, FastAPI, OpenAI API, FAISS, LangChain}}{2025}
\resumeItemListStart
\vspace{2pt}
\resumeItem{Built a \textbf{retrieval-augmented generation (RAG)} assistant using FAISS vector search,
semantic chunking, and GPT-based response generation; served via FastAPI with sub-second retrieval
latency.}
\resumeItemListEnd

\vspace{-16pt}

\resumeProjectHeading
  {\textbf{Autonomous Job Application Agent}
   $|$ \emph{Python, FastAPI, Gemini, PostgreSQL, Streamlit}}{2025}
\resumeItemListStart
\vspace{2pt}
\resumeItem{End-to-end AI agent that scrapes job listings, scores role fit with \textbf{Gemini},
generates tailored cover letters via LLM prompting, and automates application submissions through a
PostgreSQL-backed pipeline.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
